---
title: "Rihanna's evolution"
output: 
  flexdashboard::flex_dashboard:
    theme: journal
    orientation: columns
    vertical_layout: fill
    
    
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(spotifyr)
library(ggplot2)
library(cowplot)
```


Inspiration {.storyboard}
=========================================

-----------------------------------------------------------------------

### Popularity of Albums


```{r}
library(tidyverse)
library(spotifyr)
album_ids <- c('4UlGauD7ROb3YbVOFMgW5u', '4FyGpObwABjn0o8Tdp7AZz', '5pvFhFt1nzE8sCbm1wjNRv','3JSWZWeTHF4HDGt5Eozdy7','4XBfFj0WYyh5mBtU61EdyY', '1Kw1bVd07oRqcjrcjQKC8T','7vN82vd1Vq44fjlhjfvHJp')
albums <- get_albums(album_ids)
album_names <- albums$name
album_popularity <- albums$popularity
album_data <- data.frame(album_names, album_popularity)
library(ggplot2)
ggplot(album_data, aes(x = album_names, y = album_popularity)) + 
  geom_bar(stat = "identity", fill = "skyblue") + 
  xlab("Album") + ylab("Popularity") + 
  ggtitle("Popularity of all of Rihanna's albums from 2005 to 2016") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

---------------------------------------------------------

Rihanna is a highly successful musician who has released numerous albums throughout her career. Her popularity can be attributed to her unique voice, catchy tunes, and her ability to continually reinvent her sound and image.

Some of her most popular albums include "Good Girl Gone Bad" (2007), "Loud" (2010), "Talk That Talk" (2011), "Unapologetic" (2012), and "Anti" (2016). "Good Girl Gone Bad" is often cited as the album that propelled Rihanna to superstardom, featuring hit singles such as "Umbrella" and "Don't Stop the Music". "Loud" was another highly successful album, featuring the chart-topping hits "Only Girl (In the World)" and "What's My Name?".

Rihanna's albums have been well received by both fans and critics. Her unique sound and style have helped her stand out in a crowded music industry, and her ability to collaborate with other artists has also helped her gain more exposure. In addition to her successful music career, Rihanna has also made a name for herself in other areas, such as fashion and beauty.

Chromatograms and self-similarity matrices{.storyboard}
=========================================

-----------------------------------------------------------------------


### Pon de Replay


```{r,fig.width=9, fig.height=6}
library(tidyverse)
library(spotifyr)
library(compmus)

bzt<-
  get_tidy_audio_analysis("4TsmezEQVSZNNPv5RJ65Ov") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
          compmus_summarise, timbre,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

bzt |>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()


bzt |>
  compmus_self_similarity(timbre, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")
```

-----------------------------------------------------------------------

Intro (0:00-0:11): The song begins with a brief intro featuring a repeating melody and Rihanna's vocals. Verse 1 (0:11-0:33): The first verse begins with Rihanna's vocals over a sparse beat, building to a more intense chorus. Chorus 1 (0:33-0:56): The first chorus features Rihanna's catchy hook " Come Mr. DJ song pon de replay," over a driving beat. Verse 2 (0:56-1:17): The second verse features a similar structure to the first verse, building to the second chorus. Chorus 2 (1:17-1:41): The second chorus is a repeat of the first chorus. Bridge (1:41-2:02): The bridge provides a contrast to the chorus, featuring a different melody and lyrics Chorus 3 (2:02-2:26): The third chorus is a repeat of the first two choruses, with a few variations in the instrumentation. Outro (2:26-3:18): The song ends with a fade-out of the chorus, featuring Rihanna's vocals and a repeating synth melody.

### Unfaithful

```{r,fig.width=9, fig.height=6}
mpt <-
  get_tidy_audio_analysis("13xxBnXOuiBxVxJI458B0i") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
          compmus_summarise, timbre,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

mpt |>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()


mpt |>
  compmus_self_similarity(timbre, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")
```

-------------------------------------------------------------------

Intro (0:00-0:19): The song begins with a slow and mournful piano melody, which sets the tone for the emotional lyrics that follow. Verse 1 (0:19-0:41): The first verse begins with Rihanna's vocals over a simple piano accompaniment, building to a more intense chorus. Chorus 1 (0:41-1:02): The first chorus features Rihanna's emotive vocals over a more layered and complex instrumental accompaniment. Verse 2 (1:02-1:24): The second verse features a similar structure to the first verse, building to the second chorus. Chorus 2 (1:24-1:45): The second chorus is a repeat of the first chorus, with slight variations in the instrumentation and vocal delivery. Bridge (1:45-2:06): The bridge provides a contrast to the chorus, featuring a different melody and lyrics, as Rihanna sings "I don't wanna be the reason why / Every time I walk out the door / I see him die a little more inside." Chorus 3 (2:06-2:27): The third chorus is a repeat of the first two choruses, with a few variations in the instrumentation. Outro (2:27-3:51): The song ends with a repetition of the intro's piano melody, with Rihanna's vocals fading out.

### Umbrella

```{r,fig.width=9, fig.height=6}
llt <-
  get_tidy_audio_analysis("49FYlytm3dAAraYgpoJZux") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
          compmus_summarise, timbre,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

llt |>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()


llt |>
  compmus_self_similarity(timbre, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")
```

----------------------------------------------------------------------

Intro (0:00-0:10): The song begins with a synth chord progression and a simple drum pattern. Verse 1 (0:10-0:43): The first verse features Rihanna's vocals over a sparse instrumental accompaniment, building to a pre-chorus. Pre-chorus (0:43-1:02): The pre-chorus begins with a slightly more intense instrumental accompaniment. Chorus 1 (1:02-1:32): The first chorus features a catchy and repetitive melody, with Rihanna's vocals over a layered and upbeat instrumental accompaniment. Verse 2 (1:32-2:06): The second verse is similar to the first verse, but with slight variations in the instrumentation and vocal delivery. Pre-chorus (2:06-2:25): The pre-chorus is repeated, leading into the second chorus. Chorus 2 (2:25-2:56): The second chorus is a repeat of the first chorus, but with some variations in the instrumentation and vocal ad-libs. Bridge (2:56-3:18): The bridge provides a contrast to the chorus, with a slower tempo and a different chord progression.Chorus 3 (3:18-3:49): The third chorus is a repeat of the first two choruses, with additional vocal ad-libs and harmonies. Outro (3:49-4:13): The song ends with a repetition of the chorus and an instrumental fade-out.

### Rude boy

```{r,fig.width=9, fig.height=6}
jkt <-
  get_tidy_audio_analysis("60jzFy6Nn4M0iD1d94oteF") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
          compmus_summarise, timbre,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

jkt |>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()


jkt |>
  compmus_self_similarity(timbre, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")
```

-----------------------------------------------------------------------


Intro (0:00-0:11): The song starts with a drum loop, a synth riff, and Rihanna's vocals.Verse 1 (0:11-0:43): The first verse features Rihanna's vocals over a sparse instrumental accompaniment, building to a pre-chorus.Pre-chorus (0:43-0:59): Starts with a more intense instrumental accompaniment.Chorus 1 (0:59-1:30): The first chorus features a catchy and repetitive melody, with Rihanna's vocals over a layered and upbeat instrumental accompaniment. Verse 2 (1:33-2:05): The second verse is similar to the first verse, but with some variations in the instrumentation and vocal delivery. Pre-chorus (2:05-2:21): The pre-chorus is repeated, leading into the second chorus. Chorus 2 (2:21-2:51): The second chorus is a repeat of the first chorus, but with some variations in the instrumentation and vocal. Bridge (2:51-3:23): The bridge provides a contrast to the chorus, with a slower tempo and a different chord progression. Chorus 3 (3:23-3:53): The third chorus is a repeat of the first two choruses, with additional vocal ad-libs and harmonies. Outro (3:53-4:16): The song ends with a repetition of the chorus and an instrumental fade-out.



### S&M

```{r,fig.width=9, fig.height=6}
lao <-
  get_tidy_audio_analysis("0C4ejWmOTMv8vuYj85mf8m") |> 
  compmus_align(bars, segments) |>                    
  select(bars) |>                                     
  unnest(bars) |>                                     
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "rms", norm = "euclidean"             
      )
  ) |>
  mutate(
    timbre =
      map(segments,
          compmus_summarise, timbre,
          method = "rms", norm = "euclidean"             
      )
  )


lao |>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()


lao |>
  compmus_self_similarity(timbre, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")
```

------------------------------------------------------------------------

Intro (0:00-0:11): The song starts with a drum loop, a synth riff, and Rihanna's vocals.Verse 1 (0:11-0:43): The first verse features Rihanna's vocals over a sparse instrumental accompaniment, building to a pre-chorus.
Pre-chorus (0:43-0:59): Starts with a more intense instrumental accompaniment.Chorus 1 (0:59-1:30): The first chorus features a catchy and repetitive melody, with Rihanna's vocals over a layered and upbeat instrumental accompaniment.Verse 2 (1:33-2:05): The second verse is similar to the first verse, but with some variations in the instrumentation and vocal delivery. Pre-chorus (2:05-2:21): The pre-chorus is repeated, leading into the second chorus. Chorus 2 (2:21-2:51): The second chorus is a repeat of the first chorus, but with some variations in the instrumentation and vocal ad-libs. Bridge (2:51-3:23): The bridge provides a contrast to the chorus, with a slower tempo and a different chord progression. Chorus 3 (3:23-3:53): The third chorus is a repeat of the first two choruses, with additional vocal ad-libs and harmonies. Outro (3:53-4:16): The song ends with a repetition of the chorus and an instrumental fade-out.

### We found love

```{r,fig.width=9, fig.height=6}
bzt<-
  get_tidy_audio_analysis("0U10zFw4GlBacOy9VDGfGL") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
          compmus_summarise, timbre,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

bzt |>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()


bzt |>
  compmus_self_similarity(timbre, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")

```

-----------------------------------------------------------------------

Intro (0:00-0:04): The song starts with a repetitive synth riff and Rihanna's vocals. Verse 1 (0:04-0:35): The first verse features Rihanna's vocals over instrumental accompaniment, building to a pre-chorus. Pre-chorus (0:35-0:49): The pre-chorus is a short section that serves as a transition from the verse to the chorus, with a more intense instrumental accompaniment. Chorus 1 (0:49-1:19): The first chorus features a catchy and repetitive melody, with Rihanna's vocals over a layered and upbeat instrumental accompaniment. Verse 2 (1:19-1:50): The second verse is similar to the first verse, but with some variations in the instrumentation and vocal delivery. Pre-chorus (1:50-2:04): The pre-chorus is repeated, leading into the second chorus. Chorus 2 (2:04-2:34): The second chorus is a repeat of the first chorus, but with some variations in the instrumentation and vocal ad-libs. Bridge (2:34-2:49): The bridge provides a contrast to the chorus, with a slower tempo. The third chorus is a repeat of the first two choruses, with additional vocal ad-libs and harmonies. Outro (3:19-3:50): The song ends with a repetition of the chorus and an instrumental fade-out.

### Diamonds

```{r,fig.width=9, fig.height=6}
library(tidyverse)
library(spotifyr)
library(compmus)

bzt<-
  get_tidy_audio_analysis("6O20JhBJPePEkBdrB5sqRx") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
          compmus_summarise, timbre,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

bzt |>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()


bzt |>
  compmus_self_similarity(timbre, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")
```

----------------------------------------------------------------

Intro (0:00-0:07): The song starts with a slow and atmospheric instrumental intro, with a repeating piano melody and Rihanna's vocals. Verse 1 (0:07-0:38): The first verse features Rihanna's vocals over a sparse instrumental accompaniment, building to a pre-chorus. Pre-chorus (0:38-0:52): The pre-chorus is a short section that serves as a transition. Chorus 1 (0:52-1:22): The first chorus features a catchy and repetitive melody, with Rihanna's vocals over a layered instrumental accompaniment. Verse 2 (1:22-1:53): The second verse is similar to the first verse, but with some variations in the instrumentation and vocal delivery. Pre-chorus (1:53-2:07): The pre-chorus is repeated, leading into the second chorus. Chorus 2 (2:07-2:38): The second chorus is a repeat of the first chorus, but with some variations in the instrumentation and vocal ad-libs. Bridge (2:38-3:09): The bridge provides a contrast to the chorus, with a slower tempo. Chorus 3 (3:09-3:39): The third chorus is a repeat of the first two choruses, with additional vocals and harmonies. Outro (3:39-4:22): The song ends with a repetition of the chorus and an instrumental fade-out.


### Work

```{r,fig.width=9, fig.height=6}
bzt<-
  get_tidy_audio_analysis("5gZsEYaYvyi1sAVyuiXbDm") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
          compmus_summarise, timbre,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

bzt |>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()


bzt |>
  compmus_self_similarity(timbre, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")
```

------------------------------------------------------------------

Intro (0:00-0:13): The song starts with a repeating instrumental riff and Rihanna's vocal ad-libs. Verse 1 (0:13-0:39): The first verse features Rihanna's vocals over an instrumental accompaniment, building to a pre-chorus. Pre-chorus (0:39-0:53): The pre-chorus is a short section that serves as a transition again. Chorus 1 (0:53-1:29): The first chorus features Rihanna's vocals over a dancehall-inspired instrumental accompaniment, with a repetitive and catchy melody. Verse 2 (1:29-1:57): The second verse is similar to the first verse, but with some variations in the instrumentation and vocal delivery. Pre-chorus (1:57-2:12): The pre-chorus is repeated, leading into the second chorus. Chorus 2 (2:12-2:49): The second chorus is a repeat of the first chorus, with some variations in the instrumentation and vocal ad-libs. Bridge (2:49-3:04): The bridge is a short section that features a contrasting instrumental accompaniment.Chorus 3 (3:04-3:42): The third chorus is a repeat of the first two choruses, with additional vocal ad-libs and harmonies. Outro (3:42-3:59): The song ends with a repetition of the chorus and an instrumental fade-out.


Chromatograms of the most streamed{.storyboard}
=====================================  

----------------------------------------------
  
### Pon De Replay 

```{r}
library(tidyverse)
library(spotifyr)
library(compmus)
wood <-
  get_tidy_audio_analysis("4TsmezEQVSZNNPv5RJ65Ov") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

wood |>
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude",title = "Pon de Replay") +
  theme_minimal() +
  scale_fill_viridis_c()

```

-----------------------------------------------------------------------

### Unfaithful
```{r}
library(tidyverse)
library(spotifyr)
library(compmus)
wood <-
  get_tidy_audio_analysis("1oh6hjPd82XlGFQGUh2Jfa") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

wood |>
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude",title = "Unfaithful") +
  theme_minimal() +
  scale_fill_viridis_c()

```

-----------------------------------------------------------------------

### Umbrella

```{r}
library(tidyverse)
library(spotifyr)
library(compmus)
wood <-
  get_tidy_audio_analysis("49FYlytm3dAAraYgpoJZux") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

wood |>
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude",title = "Umbrella") +
  theme_minimal() +
  scale_fill_viridis_c()

```

-----------------------------------------------------------------------

### Rude Boy
```{r}
library(tidyverse)
library(spotifyr)
library(compmus)
wood <-
  get_tidy_audio_analysis("60jzFy6Nn4M0iD1d94oteF") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

wood |>
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude",title = "Rude Boy") +
  theme_minimal() +
  scale_fill_viridis_c()

```

-----------------------------------------------------------------------

### S&M

```{r}
library(tidyverse)
library(spotifyr)
library(compmus)
wood <-
  get_tidy_audio_analysis("7ySUcLPVX7KudhnmNcgY2D") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

wood |>
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude",title = "S%M") +
  theme_minimal() +
  scale_fill_viridis_c()

```

-----------------------------------------------------------------------

### We found love

```{r}
library(tidyverse)
library(spotifyr)
library(compmus)

where <-
  get_tidy_audio_analysis (c("3t4HeVfURZ5DuqMWz0Cmqg")) |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

where |>
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude",title = "We Found Love") +
  theme_minimal() +
  scale_fill_viridis_c()
```

-----------------------------------------------------------------------

### Diamonds

```{r}
where <-
  get_tidy_audio_analysis (c("5pDUMdIiW0rNLzFryqpC9j")) |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

where |>
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude",title = "Diamonds") +
  theme_minimal() +
  scale_fill_viridis_c()

```

-----------------------------------------------------------------------

### Work

```{r}

library(tidyverse)
library(spotifyr)
library(compmus)

where <-
  get_tidy_audio_analysis (c("72TFWvU3wUYdUuxejTTIzt")) |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

where |>
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude",title = "Work") +
  theme_minimal() +
  scale_fill_viridis_c()
```

-----------------------------------------------------------------------



Chordograms{.storyboard}
=========================================

-----------------------------------------------------------------------

### Pon de replay
  
  ```{r}
library(tidyverse)
library(spotifyr)
library(compmus)


circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )


pondereplay <-
  get_tidy_audio_analysis("4TsmezEQVSZNNPv5RJ65Ov") |>
  compmus_align(sections, segments) |>
  select(sections) |>
  unnest(sections) |>
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      )
  )


pondereplay |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")

```

------------------------------------------------------------------------

"Pon de Replay" by Rihanna is a popular dancehall-influenced pop song. The song is primarily in the key of B-flat minor, with a tempo of approximately 100 beats per minute.The chord progression in the song is relatively simple and features a repeating pattern of three chords throughout most of the song. The chords used in "Pon de Replay" are Bb minor, Eb minor, and F# major.

### Unfaithful

```{r}
library(tidyverse)
library(spotifyr)
library(compmus)


circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )


unfaith <-
  get_tidy_audio_analysis("1oh6hjPd82XlGFQGUh2Jfa") |>
  compmus_align(sections, segments) |>
  select(sections) |>
  unnest(sections) |>
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      )
  )


unfaith |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")
```

-----------------------------------------------------------------------

"Unfaithful" by Rihanna is a pop ballad that features a piano-based accompaniment with a simple yet powerful harmonic structure. The song is primarily in the key of C minor, with a tempo of approximately 90 beats per minute.The chord progression in "Unfaithful" is relatively simple, featuring a repeating pattern of four chords throughout the song. The chords used in "Unfaithful" are C minor, Bb major, Ab major, and G major.

### Umbrella

  ```{r}

library(tidyverse)
library(spotifyr)
library(compmus)


circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )


umbrella <-
  get_tidy_audio_analysis("49FYlytm3dAAraYgpoJZux") |>
  compmus_align(sections, segments) |>
  select(sections) |>
  unnest(sections) |>
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      )
  )


umbrella |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")

```

----------------------------------------------------------------------

"Umbrella" by Rihanna is a pop song with R&B and hip-hop influences. The song is primarily in the key of C# minor, with a tempo of approximately 87 beats per minute.The chord progression in "Umbrella" is relatively simple, featuring a repeating pattern of three chords throughout most of the song. The chords used in "Umbrella" are C# minor, B major, and A major.



### Rude Boy

  
  
  ```{r}
library(tidyverse)
library(spotifyr)
library(compmus)


circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )


rudeboy <-
  get_tidy_audio_analysis("60jzFy6Nn4M0iD1d94oteF") |>
  compmus_align(sections, segments) |>
  select(sections) |>
  unnest(sections) |>
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      )
  )


rudeboy |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")
```

-------------------------------------------------------------------------

"Rude Boy" by Rihanna is a dancehall and reggae-influenced pop song. The song is primarily in the key of B minor, with a tempo of approximately 87 beats per minute.The chord progression in "Rude Boy" is relatively simple, featuring a repeating pattern of four chords throughout most of the song. The chords used in "Rude Boy" are B minor, D major, G major, and A major.  

### S&M

 ```{r}
library(tidyverse)
library(spotifyr)
library(compmus)


circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )


snm <-
  get_tidy_audio_analysis("0C4ejWmOTMv8vuYj85mf8m") |>
  compmus_align(sections, segments) |>
  select(sections) |>
  unnest(sections) |>
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      )
  )


snm |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")
```

--------------------------------------------------------------

"S&M" by Rihanna is an electro-pop and dance-pop song with influences from house and techno music. The song is primarily in the key of E-flat major, with a tempo of approximately 128 beats per minute.The chord progression in "S&M" is relatively simple, featuring a repeating pattern of four chords throughout most of the song. The chords used in "S&M" are E-flat major, B-flat major, C minor, and G minor.



### We found love 

  
  
  ```{r}
library(tidyverse)
library(spotifyr)
library(compmus)


circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )


wefoundlove <-
  get_tidy_audio_analysis("0U10zFw4GlBacOy9VDGfGL") |>
  compmus_align(sections, segments) |>
  select(sections) |>
  unnest(sections) |>
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      )
  )


wefoundlove |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")

```

-------------------------------------------------------------------------

 "We Found Love" by Rihanna is an upbeat dance-pop and EDM song with influences from house and techno music. The song is primarily in the key of G major, with a tempo of approximately 128 beats per minute.The chord progression in "We Found Love" is relatively simple, featuring a repeating pattern of four chords throughout most of the song. The chords used in "We Found Love" are G major, D major, Em, and C major.
 

### Diamonds

  
  
  ```{r}
library(tidyverse)
library(spotifyr)
library(compmus)


circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )


diamonds <-
  get_tidy_audio_analysis("5pDUMdIiW0rNLzFryqpC9j") |>
  compmus_align(sections, segments) |>
  select(sections) |>
  unnest(sections) |>
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      )
  )


diamonds |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")
```

-------------------------------------------------------------------------

"Diamonds" by Rihanna is a mid-tempo pop ballad with a prominent piano riff and a chorus that features electronic beats. The song is primarily in the key of B-flat major, with a tempo of approximately 92 beats per minute.The chord progression in "Diamonds" is relatively simple, featuring a repeating pattern of four chords throughout most of the song. The chords used in "Diamonds" are B-flat major, G minor, E-flat major, and F major.

  
### Work

  
  
  ```{r}
library(tidyverse)
library(spotifyr)
library(compmus)


circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )


work <-
  get_tidy_audio_analysis("5gZsEYaYvyi1sAVyuiXbDm") |>
  compmus_align(sections, segments) |>
  select(sections) |>
  unnest(sections) |>
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      )
  )


work |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")
```

-----------------------------------------------------------------------

"Work" by Rihanna is a dancehall-inspired pop song with a prominent beat and lyrics. The song is primarily in the key of A minor, with a tempo of approximately 92 beats per minute.The chord progression in "Work" is relatively simple, featuring a repeating pattern of four chords throughout most of the song. The chords used in "Work" are A minor, E minor, D major, and F major.   

  
  

Fourier-based tempograms{.storyboard}
=====================================  

----------------------------------------------


### Pon de Replay

```{r}

pondrpl <- get_tidy_audio_analysis("4TsmezEQVSZNNPv5RJ65Ov")

pondrpl |>
  tempogram(window_size = 8, hop_size = 1, cyclic = TRUE) |>
  ggplot(aes(x = time, y = bpm, fill = power)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic()
```

--------------------------------------------------------------

"Pon de Replay" by Rihanna has a specific tempo of around  99/100  beats per minute (BPM). The  tempo falls within the range of what is considered a mid-tempo song, which can be described as having a moderate pace that is neither too fast nor too slow. The steady beat of 99 BPM in "Pon de Replay" gives the song a catchy and danceable feel, which possibly helped make it a hit when it was released in 2005

### Unfaithful 

```{r}
unfaith <- get_tidy_audio_analysis("1oh6hjPd82XlGFQGUh2Jfa")

unfaith |>
  tempogram(window_size = 8, hop_size = 1, cyclic = TRUE) |>
  ggplot(aes(x = time, y = bpm, fill = power)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic()
```

--------------------------------------------------------------

"Unfaithful" by Rihanna has a tempo of 90 beats per minute (BPM). This tempo also falls within the range of what is typically considered a mid-tempo song, which can be described as having a moderate pace that is again neither too fast nor too slow. The tempo of 90 BPM in "Unfaithful"  however is  slower than the tempo of Rihanna's earlier hit "Pon de Replay", which has a tempo of 99 BPM. The slower tempo of "Unfaithful" gives the song a more contemplative and melancholy feel, which suits the song's subject matter of a troubled relationship..

### Umbrella

```{r}
umbr <- get_tidy_audio_analysis("49FYlytm3dAAraYgpoJZux")

umbr |>
  tempogram(window_size = 8, hop_size = 1, cyclic = TRUE) |>
  ggplot(aes(x = time, y = bpm, fill = power)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic()
```

--------------------------------------------------------------

"Umbrella" by Rihanna has a tempo of 87 beats per minute (BPM). This tempo falls within the range of what is again  typically considered a mid-tempo song. The tempo of 87 BPM in "Umbrella" is slower than the tempo of Rihanna's earlier hit "Pon de Replay" (99 BPM) but slightly faster than the tempo of "Unfaithful" (90 BPM).
The steady beat of 87 BPM in "Umbrella" gives the song a relaxed and catchy feel, which made it a hit when it was released in 2007. Additionally, the use of a simple but memorable drum pattern and bassline throughout the song, combined with Rihanna's vocal performance, contributed  to the song's overall rhythmic groove.


### Rude Boy

```{r}

rud <- get_tidy_audio_analysis("60jzFy6Nn4M0iD1d94oteF")

rud |>
  tempogram(window_size = 8, hop_size = 1, cyclic = TRUE) |>
  ggplot(aes(x = time, y = bpm, fill = power)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic()
```

--------------------------------------------------------------

"Rude Boy" by Rihanna has a specific tempo of 87  beats per minute (BPM). This tempo falls again within  the range of what is typically considered a mid-tempo song. The tempo of 87 BPM in "Rude Boy" is the same as the tempo of Rihanna's hit "Umbrella" and is slightly slower than the tempo of her earlier hit "Pon de Replay" (99 BPM).The steady beat of 87 BPM in "Rude Boy" gives the song a danceable and infectious feel, which  made it a hit when it was released in 2010. The song features a syncopated rhythm and a catchy melody, with Rihanna's vocal performance emphasizing the song's upbeat and playful nature. The tempo of "Rude Boy" contributes to its overall energy and groove, making it a popular dance track.

### S&M

```{r}
snm <- get_tidy_audio_analysis("7ySUcLPVX7KudhnmNcgY2D")

snm |>
  tempogram(window_size = 8, hop_size = 1, cyclic = TRUE) |>
  ggplot(aes(x = time, y = bpm, fill = power)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic()
```

----------------------------------------------------------------
 
"S&M" by Rihanna has a unique  tempo of 129 beats per minute (BPM), considering the previous tracks. This tempo can be considered as a  fast-paced song, which can be described as having a quick pace that is energetic and upbeat. The tempo of 129 BPM in "S&M" is notably faster than the tempos of Rihanna's earlier hits "Unfaithful" (90 BPM) and "Umbrella" (87 BPM), and also faster than her mid-tempo hit "Rude Boy" (87 BPM). The fast tempo of "S&M" gives the song a frenetic and exciting feel, which helps to emphasize the song's provocative lyrics and playful tone. The song features a strong beat, with a driving bassline and percussion elements that add to its overall energy. The song also features the use of electronic and synthesizer elements which contribute to its overall sound and production. 

### We found love


```{r}

wefound <- get_tidy_audio_analysis("0U10zFw4GlBacOy9VDGfGL")

wefound |>
  tempogram(window_size = 8, hop_size = 1, cyclic = TRUE) |>
  ggplot(aes(x = time, y = bpm, fill = power)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic()
```

------------------------------------------------------------

"We Found Love" by Rihanna has a specific tempo of 128 beats per minute (BPM). This tempo also  falls within the range of what is typically considered a fast-paced song. The tempo of 128 BPM in "We Found Love" is similar to the tempo of Rihanna's hit "S&M" (129 BPM). The fast tempo of "We Found Love"  gives the song a pulsing and driving feel, which helps to emphasize the song's theme of an intense and passionate love affair. The song features a strong beat, with electronic and synthesizer elements that create a danceable and hypnotic sound. The tempo, combined with the song's memorable melody and Rihanna's emotive vocal performance, helped make "We Found Love" a hit when it was released in 2011. The song's tempo also is very  popular in dance clubs and on dance music charts, EDM  is typically featured.


### Diamonds 

```{r}
diam <- get_tidy_audio_analysis("5pDUMdIiW0rNLzFryqpC9j")

diam |>
  tempogram(window_size = 8, hop_size = 1, cyclic = TRUE) |>
  ggplot(aes(x = time, y = bpm, fill = power)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic()

```

--------------------------------------------------------------------

"Diamonds" by Rihanna has a tempo of 92 beats per minute (BPM). This tempo falls again within the range of mid-tempo song, which can be described. The tempo of 92 BPM in "Diamonds" is similar to the tempo of Rihanna's earlier hit "Unfaithful" (90 BPM).The moderate tempo of "Diamonds" gives the song a dreamy and contemplative feel, which emphasizes the song's theme of finding hope and strength in difficult times. The song features a pulsing beat, with electronic and percussion elements that add to its overall energy. Additionally, the song's memorable melody and Rihanna's emotive vocal performance contribute to its overall impact as a powerful and emotional ballad. 


### Work 

```{r}
library(tidyverse)
library(spotifyr)
library(compmus)



work <- get_tidy_audio_analysis("5gZsEYaYvyi1sAVyuiXbDm")

work |>
  tempogram(window_size = 8, hop_size = 1, cyclic = TRUE) |>
  ggplot(aes(x = time, y = bpm, fill = power)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic()
```

-----------------------------------------------------------------------

"Work" by Rihanna has a specific tempo of 92 beats per minute (BPM). This tempo falls again  within the range of what is typically considered a mid-tempo song. The tempo of 92 BPM in "Work" is the same as the tempo of Rihanna's earlier hit "Diamonds".The steady beat of 92 BPM in "Work" gives the song a danceable feel. The song features a repetitive, syncopated rhythm and a catchy melody, with Rihanna's vocal performance emphasizing the song's upbeat and playful nature. Additionally, the song features elements of Caribbean music, including dancehall and reggae, which contribute to its overall sound and production.

