---
title: "Rihanna's evolution"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    
---

Inspiration {.storyboard}
=========================================

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(spotifyr)
library(ggplot2)
library(cowplot)
```


-----------------------------------------------------------------------

### Popularity of Albums


```{r}
library(tidyverse)
library(spotifyr)
album_ids <- c('4UlGauD7ROb3YbVOFMgW5u', '4FyGpObwABjn0o8Tdp7AZz', '5pvFhFt1nzE8sCbm1wjNRv','3JSWZWeTHF4HDGt5Eozdy7','4XBfFj0WYyh5mBtU61EdyY', '1Kw1bVd07oRqcjrcjQKC8T','7vN82vd1Vq44fjlhjfvHJp')
albums <- get_albums(album_ids)
album_names <- albums$name
album_popularity <- albums$popularity
album_data <- data.frame(album_names, album_popularity)
library(ggplot2)
ggplot(album_data, aes(x = album_names, y = album_popularity)) + 
  geom_bar(stat = "identity", fill = "skyblue") + 
  xlab("Album") + ylab("Popularity") + 
  ggtitle("Popularity of all of Rihanna's albums from 2005 to 2016") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

---------------------------------------------------------

Rihanna is a highly successful musician who has released numerous albums throughout her career. Her popularity can be attributed to her unique voice, catchy tunes, and her ability to continually reinvent her sound and image.

Some of her most popular albums include "Good Girl Gone Bad" (2007), "Loud" (2010), "Talk That Talk" (2011), "Unapologetic" (2012), and "Anti" (2016). "Good Girl Gone Bad" is often cited as the album that propelled Rihanna to superstardom, featuring hit singles such as "Umbrella" and "Don't Stop the Music". "Loud" was another highly successful album, featuring the chart-topping hits "Only Girl (In the World)" and "What's My Name?".

Rihanna's albums have been well received by both fans and critics. Her unique sound and style have helped her stand out in a crowded music industry, and her ability to collaborate with other artists has also helped her gain more exposure. In addition to her successful music career, Rihanna has also made a name for herself in other areas, such as fashion and beauty.



Cepstrograms and Self-Similarity Matrices
=====================================  

###Pon de Replay
Features of Rihanna's Pon de Replay Intro (0:00-0:11): The song begins with a brief intro featuring a repeating synth melody and Rihanna's vocals. Verse 1 (0:11-0:33): The first verse begins with Rihanna's vocals over a sparse beat, building to a more intense chorus. Chorus 1 (0:33-0:56): The first chorus features Rihanna's catchy hook "Come Mr. DJ song pon de replay," over a driving beat. Verse 2 (0:56-1:17): The second verse features a similar structure to the first verse, building to the second chorus. Chorus 2 (1:17-1:41): The second chorus is a repeat of the first chorus. Bridge (1:41-2:02): The bridge provides a contrast to the chorus, featuring a different melody and lyrics Chorus 3 (2:02-2:26): The third chorus is a repeat of the first two choruses, with a few variations in the instrumentation. Outro (2:26-3:18): The song ends with a fade-out of the chorus, featuring Rihanna's vocals and a repeating synth melody.

Overall, the arrangement of "Pon de Replay" follows a traditional pop song structure, with an intro, verses, chorus, bridge, and outro, with each section building on the previous one to create a dynamic and engaging song.

```{r}
library(tidyverse)
library(spotifyr)
library(compmus)

bzt<-
  get_tidy_audio_analysis("4TsmezEQVSZNNPv5RJ65Ov") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
          compmus_summarise, timbre,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

bzt |>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()


bzt |>
  compmus_self_similarity(timbre, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")
```

###Unfaithful

Intro (0:00-0:19): The song begins with a slow and mournful piano melody, which sets the tone for the emotional lyrics that follow. Verse 1 (0:19-0:41): The first verse begins with Rihanna's vocals over a simple piano accompaniment, building to a more intense chorus. Chorus 1 (0:41-1:02): The first chorus features Rihanna's emotive vocals over a more layered and complex instrumental accompaniment. Verse 2 (1:02-1:24): The second verse features a similar structure to the first verse, building to the second chorus. Chorus 2 (1:24-1:45): The second chorus is a repeat of the first chorus, with slight variations in the instrumentation and vocal delivery. Bridge (1:45-2:06): The bridge provides a contrast to the chorus, featuring a different melody and lyrics, as Rihanna sings "I don't wanna be the reason why / Every time I walk out the door / I see him die a little more inside." Chorus 3 (2:06-2:27): The third chorus is a repeat of the first two choruses, with a few variations in the instrumentation. Outro (2:27-3:51): The song ends with a repetition of the intro's piano melody, with Rihanna's vocals fading out.

Overall, the arrangement of "Unfaithful" follows a traditional pop ballad structure, with an intro, verses, choruses, and a bridge, with each section building on the previous one to create a dynamic and emotional song.\



```{r}
mpt <-
  get_tidy_audio_analysis("13xxBnXOuiBxVxJI458B0i") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
          compmus_summarise, timbre,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

mpt |>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()


mpt |>
  compmus_self_similarity(timbre, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")
```

###Umbrella

Intro (0:00-0:10): The song begins with a synth chord progression and a simple drum pattern. Verse 1 (0:10-0:43): The first verse features Rihanna's vocals over a sparse instrumental accompaniment, building to a pre-chorus. Pre-chorus (0:43-1:02): The pre-chorus begins with a slightly more intense instrumental accompaniment. Chorus 1 (1:02-1:32): The first chorus features a catchy and repetitive melody, with Rihanna's vocals over a layered and upbeat instrumental accompaniment. Verse 2 (1:32-2:06): The second verse is similar to the first verse, but with slight variations in the instrumentation and vocal delivery. Pre-chorus (2:06-2:25): The pre-chorus is repeated, leading into the second chorus. Chorus 2 (2:25-2:56): The second chorus is a repeat of the first chorus, but with some variations in the instrumentation and vocal ad-libs. Bridge (2:56-3:18): The bridge provides a contrast to the chorus, with a slower tempo and a different chord progression. Rihanna sings "You can run into my arms / It's okay, don't be alarmed / Come into me / There's no distance in between our love." Chorus 3 (3:18-3:49): The third chorus is a repeat of the first two choruses, with additional vocal ad-libs and harmonies. Outro (3:49-4:13): The song ends with a repetition of the chorus and an instrumental fade-out.

```{r}
llt <-
  get_tidy_audio_analysis("49FYlytm3dAAraYgpoJZux") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
          compmus_summarise, timbre,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

llt |>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()


llt |>
  compmus_self_similarity(timbre, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")
```

###Rude boy

Intro (0:00-0:11): The song starts with a drum loop, a synth riff, and Rihanna's vocals. Verse 1 (0:11-0:43): The first verse features Rihanna's vocals over a sparse instrumental accompaniment, building to a pre-chorus. Pre-chorus (0:43-0:59): Starts with a more intense instrumental accompaniment. Chorus 1 (0:59-1:30): The first chorus features a catchy and repetitive melody, with Rihanna's vocals over a layered and upbeat instrumental accompaniment. Verse 2 (1:30-2:03): The second verse is similar to the first verse, but with some variations in the instrumentation and vocal delivery. Pre-chorus (2:03-2:19): The pre-chorus is repeated, leading into the second chorus. Chorus 2 (2:19-2:50): The second chorus is a repeat of the first chorus, but with some variations in the instrumentation and vocal ad-libs. Bridge (2:50-3:12): The bridge provides a contrast to the chorus, with a slower tempo and a different chord progression. Rihanna sings "Come here rude boy, boy, can you get it up? / Come here rude boy, boy, is you big enough? / Take it, take it, baby, baby / Take it, take it, love me, love me." Chorus 3 (3:12-3:43): The third chorus is a repeat of the first two choruses, with additional vocal ad-libs and harmonies. Outro (3:43-3:57): The song ends with a repetition of the chorus and an instrumental fade-out.

Overall, the song features variations, such as the repetition of the pre-chorus and the vocal ad-libs and harmonies in the choruses. The bridge adds to the dynamic and memorable quality of the song by providing a contrast to the chorus.

```{r}
jkt <-
  get_tidy_audio_analysis("60jzFy6Nn4M0iD1d94oteF") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
          compmus_summarise, timbre,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

jkt |>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()


jkt |>
  compmus_self_similarity(timbre, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")
```

###S&M

Verse 2 (1:33-2:05): The second verse is similar to the first verse, but with some variations in the instrumentation and vocal delivery. Pre-chorus (2:05-2:21): The pre-chorus is repeated, leading into the second chorus. Chorus 2 (2:21-2:51): The second chorus is a repeat of the first chorus, but with some variations in the instrumentation and vocal ad-libs. Bridge (2:51-3:23): The bridge provides a contrast to the chorus, with a slower tempo and a different chord progression. Chorus 3 (3:23-3:53): The third chorus is a repeat of the first two choruses, with additional vocal ad-libs and harmonies. Outro (3:53-4:16): The song ends with a repetition of the chorus and an instrumental fade-out.

Overall, the arrangement of "S&M" follows a standard pop song structure, with an intro, verses, pre-choruses, choruses, and a bridge. The song features variations, such as the repetition of the pre-chorus and the vocal ad-libs and harmonies in the choruses. The bridge adds to the dynamic and memorable quality of the song by providing a contrast to the chorus.

```{r}
lao <-
  get_tidy_audio_analysis("0C4ejWmOTMv8vuYj85mf8m") |> 
  compmus_align(bars, segments) |>                    
  select(bars) |>                                     
  unnest(bars) |>                                     
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "rms", norm = "euclidean"             
      )
  ) |>
  mutate(
    timbre =
      map(segments,
          compmus_summarise, timbre,
          method = "rms", norm = "euclidean"             
      )
  )


lao |>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()


lao |>
  compmus_self_similarity(timbre, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")
```

##We found love

```{r}
bzt<-
  get_tidy_audio_analysis("0U10zFw4GlBacOy9VDGfGL") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
          compmus_summarise, timbre,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

bzt |>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()


bzt |>
  compmus_self_similarity(timbre, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")

```

Intro (0:00-0:04): The song starts with a repetitive synth riff and Rihanna's vocals. Verse 1 (0:04-0:35): The first verse features Rihanna's vocals over instrumental accompaniment, building to a pre-chorus. Pre-chorus (0:35-0:49): The pre-chorus is a short section that serves as a transition from the verse to the chorus, with a more intense instrumental accompaniment. Chorus 1 (0:49-1:19): The first chorus features a catchy and repetitive melody, with Rihanna's vocals over a layered and upbeat instrumental accompaniment. Verse 2 (1:19-1:50): The second verse is similar to the first verse, but with some variations in the instrumentation and vocal delivery. Pre-chorus (1:50-2:04): The pre-chorus is repeated, leading into the second chorus. Chorus 2 (2:04-2:34): The second chorus is a repeat of the first chorus, but with some variations in the instrumentation and vocal ad-libs. Bridge (2:34-2:49): The bridge provides a contrast to the chorus, with a slower tempo and a different chord progression. Rihanna sings "Yellow diamonds in the light / And we're standing side by side." Chorus 3 (2:49-3:19): The third chorus is a repeat of the first two choruses, with additional vocal ad-libs and harmonies. Outro (3:19-3:50): The song ends with a repetition of the chorus and an instrumental fade-out.

Overall, the arrangement of "We Found Love" follows a standard pop song structure, with an intro, verses, pre-choruses, choruses, and a bridge. The song features variations, such as the repetition of the pre-chorus and the vocal ad-libs and harmonies in the choruses. The bridge adds to the dynamic and memorable quality of the song by providing a contrast to the chorus.

##Diamonds

```{r}
library(tidyverse)
library(spotifyr)
library(compmus)

bzt<-
  get_tidy_audio_analysis("6O20JhBJPePEkBdrB5sqRx") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
          compmus_summarise, timbre,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

bzt |>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()


bzt |>
  compmus_self_similarity(timbre, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")
```

Intro (0:00-0:07): The song starts with a slow and atmospheric instrumental intro, with a repeating piano melody and Rihanna's vocals. Verse 1 (0:07-0:38): The first verse features Rihanna's vocals over a sparse instrumental accompaniment, building to a pre-chorus. Pre-chorus (0:38-0:52): The pre-chorus is a short section that serves as a transition from the verse to the chorus, with a more intense instrumental accompaniment. Chorus 1 (0:52-1:22): The first chorus features a catchy and repetitive melody, with Rihanna's vocals over a layered and upbeat instrumental accompaniment. Verse 2 (1:22-1:53): The second verse is similar to the first verse, but with some variations in the instrumentation and vocal delivery. Pre-chorus (1:53-2:07): The pre-chorus is repeated, leading into the second chorus. Chorus 2 (2:07-2:38): The second chorus is a repeat of the first chorus, but with some variations in the instrumentation and vocal ad-libs. Bridge (2:38-3:09): The bridge provides a contrast to the chorus, with a slower tempo and a different chord progression. Rihanna sings "So shine bright, tonight you and I / We're beautiful like diamonds in the sky." Chorus 3 (3:09-3:39): The third chorus is a repeat of the first two choruses, with additional vocal ad-libs and harmonies. Outro (3:39-4:22): The song ends with a repetition of the chorus and an instrumental fade-out.

Overall, the arrangement of "Diamonds" follows a standard pop song structure, with an intro, verses, pre-choruses, choruses, and a bridge. The song features variations, such as the repetition of the pre-chorus and the vocal ad-libs and harmonies in the choruses. The bridge adds to the dynamic and memorable quality of the song by providing a contrast to the chorus.

##Work

```{r}
bzt<-
  get_tidy_audio_analysis("5gZsEYaYvyi1sAVyuiXbDm") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
          compmus_summarise, timbre,
          method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

bzt |>
  compmus_gather_timbre() |>
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()


bzt |>
  compmus_self_similarity(timbre, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "")
```

"Work" by Rihanna is a dancehall and reggae-pop influenced song that follows a non-traditional pop song structure. Here is the arrangement of the song based on the most common sources:

Intro (0:00-0:13): The song starts with a repeating instrumental riff and Rihanna's vocal ad-libs. Verse 1 (0:13-0:39): The first verse features Rihanna's vocals in Jamaican Patois over a sparse instrumental accompaniment, building to a pre-chorus. Pre-chorus (0:39-0:53): The pre-chorus is a short section that serves as a transition from the verse to the chorus, with a more intense instrumental accompaniment. Chorus 1 (0:53-1:29): The first chorus features Rihanna's vocals over a dancehall-inspired instrumental accompaniment, with a repetitive and catchy melody. Verse 2 (1:29-1:57): The second verse is similar to the first verse, but with some variations in the instrumentation and vocal delivery. Pre-chorus (1:57-2:12): The pre-chorus is repeated, leading into the second chorus. Chorus 2 (2:12-2:49): The second chorus is a repeat of the first chorus, with some variations in the instrumentation and vocal ad-libs. Bridge (2:49-3:04): The bridge is a short section that features a contrasting instrumental accompaniment and Rihanna's vocals in English, singing "You see me I be work, work, work, work, work, work." Chorus 3 (3:04-3:42): The third chorus is a repeat of the first two choruses, with additional vocal ad-libs and harmonies. Outro (3:42-3:59): The song ends with a repetition of the chorus and an instrumental fade-out.

Overall, the arrangement of "Work" follows a non-traditional pop song structure, with an intro, verses, pre-choruses, choruses, and a bridge. The song features variations, such as the use of Jamaican Patois in the verses and the dancehall-inspired instrumental accompaniment. The bridge adds to the dynamic and memorable quality of the song by providing a contrast to the chorus.

Chromatograms
=====================================  
###Chromatograms of the most streamed songs of Rihanna per album 

```{r}

library(tidyverse)
library(spotifyr)
library(compmus)
wood <-
  get_tidy_audio_analysis("4TsmezEQVSZNNPv5RJ65Ov") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

wood |>
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude",title = "Pon de Replay") +
  theme_minimal() +
  scale_fill_viridis_c()

library(tidyverse)
library(spotifyr)
library(compmus)
wood <-
  get_tidy_audio_analysis("1oh6hjPd82XlGFQGUh2Jfa") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

wood |>
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude",title = "Unfaithful") +
  theme_minimal() +
  scale_fill_viridis_c()



library(tidyverse)
library(spotifyr)
library(compmus)
wood <-
  get_tidy_audio_analysis("49FYlytm3dAAraYgpoJZux") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

wood |>
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude",title = "Umbrella") +
  theme_minimal() +
  scale_fill_viridis_c()
  

library(tidyverse)
library(spotifyr)
library(compmus)
wood <-
  get_tidy_audio_analysis("60jzFy6Nn4M0iD1d94oteF") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

wood |>
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude",title = "Rude Boy") +
  theme_minimal() +
  scale_fill_viridis_c()


library(tidyverse)
library(spotifyr)
library(compmus)
wood <-
  get_tidy_audio_analysis("7ySUcLPVX7KudhnmNcgY2D") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

wood |>
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude",title = "S%M") +
  theme_minimal() +
  scale_fill_viridis_c()
  
  

library(tidyverse)
library(spotifyr)
library(compmus)

where <-
  get_tidy_audio_analysis (c("3t4HeVfURZ5DuqMWz0Cmqg")) |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

where |>
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude",title = "We Found Love") +
  theme_minimal() +
  scale_fill_viridis_c()
  
  
  

library(tidyverse)
library(spotifyr)
library(compmus)

where <-
  get_tidy_audio_analysis (c("5pDUMdIiW0rNLzFryqpC9j")) |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

where |>
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude",title = "Diamonds") +
  theme_minimal() +
  scale_fill_viridis_c()
  
  


library(tidyverse)
library(spotifyr)
library(compmus)

where <-
  get_tidy_audio_analysis (c("72TFWvU3wUYdUuxejTTIzt")) |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

where |>
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude",title = "Work") +
  theme_minimal() +
  scale_fill_viridis_c()
  
```




Pon de replay
===================================== 

```{r}
library(tidyverse)
library(spotifyr)
library(compmus)


circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )


pondereplay <-
  get_tidy_audio_analysis("4TsmezEQVSZNNPv5RJ65Ov") |>
  compmus_align(sections, segments) |>
  select(sections) |>
  unnest(sections) |>
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      )
  )


pondereplay |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")

```

-----------------------------


Unfaithful
===================================== 


```{r}
library(tidyverse)
library(spotifyr)
library(compmus)


circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )


unfaith <-
  get_tidy_audio_analysis("1oh6hjPd82XlGFQGUh2Jfa") |>
  compmus_align(sections, segments) |>
  select(sections) |>
  unnest(sections) |>
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      )
  )


unfaith |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")
```




Umbrella
===================================== 


```{r}

library(tidyverse)
library(spotifyr)
library(compmus)


circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )


umbrella <-
  get_tidy_audio_analysis("49FYlytm3dAAraYgpoJZux") |>
  compmus_align(sections, segments) |>
  select(sections) |>
  unnest(sections) |>
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      )
  )


umbrella |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")

```



Rude Boy
===================================== 


```{r}
library(tidyverse)
library(spotifyr)
library(compmus)


circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )


rudeboy <-
  get_tidy_audio_analysis("60jzFy6Nn4M0iD1d94oteF") |>
  compmus_align(sections, segments) |>
  select(sections) |>
  unnest(sections) |>
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      )
  )


rudeboy |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")
```



S&M
===================================== 


```{r}
library(tidyverse)
library(spotifyr)
library(compmus)


circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )


snm <-
  get_tidy_audio_analysis("0C4ejWmOTMv8vuYj85mf8m") |>
  compmus_align(sections, segments) |>
  select(sections) |>
  unnest(sections) |>
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      )
  )


snm |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")
```




We found love 
===================================== 


```{r}
library(tidyverse)
library(spotifyr)
library(compmus)


circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )


wefoundlove <-
  get_tidy_audio_analysis("0U10zFw4GlBacOy9VDGfGL") |>
  compmus_align(sections, segments) |>
  select(sections) |>
  unnest(sections) |>
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      )
  )


wefoundlove |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")
  
```



Diamonds
===================================== 



```{r}
library(tidyverse)
library(spotifyr)
library(compmus)


circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )


diamonds <-
  get_tidy_audio_analysis("5pDUMdIiW0rNLzFryqpC9j") |>
  compmus_align(sections, segments) |>
  select(sections) |>
  unnest(sections) |>
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      )
  )


diamonds |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")
```


Work
===================================== 



```{r}
library(tidyverse)
library(spotifyr)
library(compmus)


circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )


work <-
  get_tidy_audio_analysis("5gZsEYaYvyi1sAVyuiXbDm") |>
  compmus_align(sections, segments) |>
  select(sections) |>
  unnest(sections) |>
  mutate(
    pitches =
      map(segments,
          compmus_summarise, pitches,
          method = "mean", norm = "manhattan"
      )
  )


work |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")
```

--------------------------------------

"Work" by Rihanna is a dancehall-inspired pop song with a prominent beat and lyrics. The song is primarily in the key of A minor, with a tempo of approximately 92 beats per minute.The chord progression in "Work" is relatively simple, featuring a repeating pattern of four chords throughout most of the song. The chords used in "Work" are A minor, E minor, D major, and F major.   



Information 
===================================== 



 
 The information is presented due to issues with visualization(size), which would hopefully be resolved soon. 



"Pon de Replay" by Rihanna is a popular dancehall-influenced pop song. The song is primarily in the key of B-flat minor, with a tempo of approximately 100 beats per minute.The chord progression in the song is relatively simple and features a repeating pattern of three chords throughout most of the song. The chords used in "Pon de Replay" are Bb minor, Eb minor, and F# major.

"Unfaithful" by Rihanna is a pop ballad that features a piano-based accompaniment with a simple yet powerful harmonic structure. The song is primarily in the key of C minor, with a tempo of approximately 90 beats per minute.The chord progression in "Unfaithful" is relatively simple, featuring a repeating pattern of four chords throughout the song. The chords used in "Unfaithful" are C minor, Bb major, Ab major, and G major.


"Umbrella" by Rihanna is a pop song with R&B and hip-hop influences. The song is primarily in the key of C# minor, with a tempo of approximately 87 beats per minute.The chord progression in "Umbrella" is relatively simple, featuring a repeating pattern of three chords throughout most of the song. The chords used in "Umbrella" are C# minor, B major, and A major.


"Rude Boy" by Rihanna is a dancehall and reggae-influenced pop song. The song is primarily in the key of B minor, with a tempo of approximately 87 beats per minute.The chord progression in "Rude Boy" is relatively simple, featuring a repeating pattern of four chords throughout most of the song. The chords used in "Rude Boy" are B minor, D major, G major, and A major.


"S&M" by Rihanna is an electro-pop and dance-pop song with influences from house and techno music. The song is primarily in the key of E-flat major, with a tempo of approximately 128 beats per minute.The chord progression in "S&M" is relatively simple, featuring a repeating pattern of four chords throughout most of the song. The chords used in "S&M" are E-flat major, B-flat major, C minor, and G minor.


"We Found Love" by Rihanna is an upbeat dance-pop and EDM song with influences from house and techno music. The song is primarily in the key of G major, with a tempo of approximately 128 beats per minute.The chord progression in "We Found Love" is relatively simple, featuring a repeating pattern of four chords throughout most of the song. The chords used in "We Found Love" are G major, D major, Em, and C major.


"Diamonds" by Rihanna is a mid-tempo pop ballad with a prominent piano riff and a chorus that features electronic beats. The song is primarily in the key of B-flat major, with a tempo of approximately 92 beats per minute.The chord progression in "Diamonds" is relatively simple, featuring a repeating pattern of four chords throughout most of the song. The chords used in "Diamonds" are B-flat major, G minor, E-flat major, and F major.


"Work" by Rihanna is a dancehall-inspired pop song with a prominent beat and lyrics. The song is primarily in the key of A minor, with a tempo of approximately 92 beats per minute.The chord progression in "Work" is relatively simple, featuring a repeating pattern of four chords throughout most of the song. The chords used in "Work" are A minor, E minor, D major, and F major.   
### Chart 1
    
```{r}
```
   
